A Data-Driven Framework for Neural Field Modeling

### 2011-01-07 ltx/first_order_framework/LaTeX_Manuscript.tex
added incremental EM reference

\mike{The estimation framework that we have presented uses an inherently batch algorithm designed to operate after data has been collected. An alternative approach, that is a natural extension of the framework, would allow for the algorithm to learn online, where techniques such as the recursive LS estimator \cite{Ljung99}, the incremental EM algorithm \cite{Neal98} or the stepwise EM \cite{Sato00,Cappe09} [see attached for details] may be used. These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.}

>>>>

\mike{The estimation framework that we have presented uses an inherently batch algorithm designed to operate after data has been collected. An alternative approach, that is a natural extension of the framework, would allow for the algorithm to learn online, where techniques such as the recursive LS estimator \cite{Ljung99}, the incremental EM algorithm \cite{Neal1998} or the stepwise EM \cite{Sato00,Cappe09} [see attached for details] may be used. These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy.}
